Exponential Random Graph Models with Big Networks: Maximum Pseudolikelihood Estimation and the Parametric Bootstrap

### 2017-07-27 TeX/conference_paper.tex
revising estimation section

\section{Estimation}
\noindent As mentioned above calculating $c(\theta)$ is not achievable for most cases with today's technology.  Straightforward application of either maximum likelihood estimation and Bayesian inference are, therefore, not possible. The first method proposed in the literature for estimating ERGM parameters was maximum pseudolikelihood estimation \cite{StraussIkeda1990}. Under maximum pseudolikelihood, the joint distribution is replaced by the product over conditional distributions \cite{besag1986statistical}.  
%
\begin{equation*}
\mathbb{P}_{\theta}(G) \approx \prod_{ij} \mathbb{P}_{\theta}\left(g_{ij}|G_{-ij}\right), 
%\label{ILogit}
\end{equation*}
where $G_{-ij}$ is the adjacency matrix, excluding element $ij$.

>>>>

\section{Estimation}
\noindent As mentioned above calculating $c(\theta)$ is not achievable for most cases with today's technology.  Straightforward application of either maximum likelihood estimation and Bayesian inference are, therefore, not possible. The first method proposed in the literature for estimating ERGM parameters was maximum pseudolikelihood estimation \cite{StraussIkeda1990}. Under maximum pseudolikelihood, the joint distribution is replaced by the product over conditional distributions \cite{besag1986statistical}.  
%
\begin{equation*}
\mathbb{P}_{\theta}(G) \approx \prod_{ij} \mathbb{P}_{\theta}\left(g_{ij}|G_{-ij}\right), 
%\label{ILogit}
\end{equation*}
where $G_{-ij}$ is the adjacency matrix, excluding element $ij$. The conditional probability of a tie in ERGM reduces, conveniently, to a logistic regression form given by 
\begin{equation*}
\mathbb{P}_{\theta}\left(g_{ij}=1| G_{-ij} \right) = \text{\\} \text{logit}^{-1}\left( \theta^T \cdot \delta(\Gamma(G))  \right), 
%\label{ILogit}
\end{equation*}
where $\delta(\Gamma(G))$ is the ``change statistic'' given by the difference in the network statistics when the $ij$ element is toggled from 0 to 1 (i.e., $\Gamma(G|g_{ij}=1))-\Gamma(G|g_{ij}=0)$), and $\text{logit}^{-1}(x)=1/(1+\exp(-x))$ \cite{goodreau2009birds}.
